\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-12 generated/assessments.tex
Revisions for Computer Journal

\citenum{ref-1} & On request\flagStyle{ } & ``Code is available upon request from the corresponding author'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-2} & ``The datasets used in the current study are available from the corresponding author upon reasonable request and under consideration of the ethical regulations''\flagStyle{ $\sf R_d$\hskip 3pt{}} & Matlab. Documented overview, but only trivial comments\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-3} & ``In accordance with Twitter policies of data sharing, data used in the generation of the algorithm for this study will not be made publicly available''\flagStyle{ } & ``Due to the sensitive and potentially stigmatizing nature of this tool, code used for algorithm generation or implementation on individual Twitter profiles will not be made publicly available''\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-4} & ``The datasets generated during and/or analyzed during the current study are available from the corresponding author on reasonable request.''``''\flagStyle{ } & ``This code would be made available upon reasonable request.'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-5} & Nothing available\flagStyle{ } & Nothing available (despite building two voice-based virtual counselors)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-6} & ``The datasets generated and analyzed during the study are not currently publicly available due to HIPAA compliance agreement but are available from the corresponding author on reasonable request''\flagStyle{ } & Poor commenting, no documentation\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-7} & ``The dataset generated and analyzed for this study will not be made publicly available due to patient privacy and lack of informed consent to allow sharing of patient data outside of the research team''\flagStyle{ } & No code available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-8} & ``The datasets generated during and/or analyzed during the current study are not publicly available due to institutional restrictions on data sharing and privacy concerns. However, the data are available from the corresponding author on reasonable request''\flagStyle{ } & Empty GitHub repository: ``Code coming soon\ldots'' it says\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf R_{\mbox{\scriptsize c-empty}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-9} & ``The i2b2 data that support the findings of this study are available from i2b2 but restrictions apply to the availability of these data, which require signed safe usage and research-only. Data from UCSF are not available at this time as they have not been legally certified as being De-Identified, however, this process is underway and the data may be available by the time of publication by contacting the authors. Requesters identity as researchers will need to be confirmed, safe usage guarantees will need to be signed, and other restrictions may apply''\flagStyle{ } & Basic documentation, very little comment\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-10} & ``Not available due to restrictions in the ethical permit, but may be available on request''\flagStyle{ } & Trivial comments, no documentation\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-11} & ``The data that support the findings of this study are available in a deidentified form from Cleveland Clinic, but restrictions apply to the availability of these data, which were used under Cleveland Clinic data policies for the current study, and so are not publicly available''\flagStyle{ } & ``We used only free and open-source software'' some of which is unspecified\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-12} & ``The i-ROP cohort study data for ROP is not publicly available due to patient privacy restrictions, though potential collaborators are directed to contact the study investigators \ldots''\flagStyle{ } & Not all code on GitHub, minor comments\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{paper-usesRMarkdown} & Data available on Dryad\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code and example runs available in R Markdown\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_{+}$\hskip 3pt{}}\\
\citenum{ref-14} & Data directly written into program code\flagStyle{ } & Basic Matlab with routine comments\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{onlyPaperWithChecks} & Data available on Dryad plus publicly available data from the 1000 genomes project. Currently (apparently) for private view\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code available for private view, though some code available with minor comments. Paper describes using two contrasting methods to help confirm correctness, ``As an additional check, I also coded the calculation of D based on a probabilistic approach, using genotype frequencies in each population to calculate the expected frequencies of each possible two-genotype combination (electronic supplementary material, table S1). Essentially identical results were obtained.'' but the contrasting method is not available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf S_{{\mbox{\scriptsize otherSE}}}$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-16} & Data available on Dryad\flagStyle{ $\sf R_d$\hskip 3pt{}} & Reasonaby commented code on Dryad, but code is not complete and presumably never checked\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-17} & On request\flagStyle{ } & R lightly commented\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ethics-paper} & No data required\flagStyle{ } & Unrunnable incomplete code fragment\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-19} & Data embedded in PDF\flagStyle{ } & No code available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-20} & Data available on Dryad\flagStyle{ $\sf R_d$\hskip 3pt{}} & Some comments, some code in Matlab\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-21} & Partial data on Dryad\flagStyle{ $\sf R_d$\hskip 3pt{}} & Documented R, including manual\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_{+}$\hskip 3pt{}}\\
\citenum{ref-22} & No data required\flagStyle{ } & ``We constructed a bioeconomic model for an RSSF [restricted fishing effort small-scale fishery] using game theory'' for which results are discussed, yet no code is available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-23} & Data cited, not all available\flagStyle{ } & Trivial documentation\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{example-numerical-error} & On Figshare\flagStyle{ $\sf R_d$\hskip 3pt{}} & On Figshare, large amount of disorganised and undocumented code. Helpful features to make usable for third parties\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-25} & Data on Dryad\flagStyle{ $\sf R_d$\hskip 3pt{}} & No code available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-26} & Data on various web sites\flagStyle{ } & No code available\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-27} & Data on request\flagStyle{ } & ``The coding used to train the artificial intelligence model are dependent on annotation, infrastructure, and hardware, so cannot be released.'' (!) Algorithm (not source code) available on request.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-28} & Data on request\flagStyle{ } & Python scripts can be requested\flagStyle{ $\sf S_p$\hskip 3pt{}}\\
\citenum{ref-29} & Unspecified location on large website requiring registration\flagStyle{ $\sf R_d$\hskip 3pt{}} & Has overall documentation but poorly commented Matlab code on GitHub\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-30} & Available to researchers who meet criteria for access to confidential data\flagStyle{ } & Despite the paper being a ``deep learning algorithm'' the code is not available\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-31} & Data access conditional on approved study proposal\flagStyle{ } & Almost completely uncommented Python, but does have a basic setup script\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-32} & Unspecified locations on several large websites\flagStyle{ } & Python used and apparently GitHub, but --- an oversight? --- no code is available\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\

>>>>

\citenum{ref-1} & On request.\flagStyle{ } & ``Code is available upon request from the corresponding author'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-2} & ``The datasets used in the current study are available from the corresponding author upon reasonable request and under consideration of the ethical regulations.''\flagStyle{ $\sf R_d$\hskip 3pt{}} & Matlab. Documented overview, but only trivial comments. Assertions in code only relate to UI.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}$\sf C_a$\hskip 3pt{}}\\
\citenum{ref-3} & ``In accordance with Twitter policies of data sharing, data used in the generation of the algorithm for this study will not be made publicly available.''\flagStyle{ } & ``Due to the sensitive and potentially stigmatizing nature of this tool, code used for algorithm generation or implementation on individual Twitter profiles will not be made publicly available.''\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-4} & ``The datasets generated during and/or analyzed during the current study are available from the corresponding author on reasonable request.''\flagStyle{ } & ``This code would be made available upon reasonable request.'' (requested)\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-5} & Nothing available\flagStyle{ } & Nothing available (despite building two voice-based virtual counselors).\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-6} & ``The datasets generated and analyzed during the study are not currently publicly available due to HIPAA compliance agreement but are available from the corresponding author on reasonable request.''\flagStyle{ } & Poor commenting, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-7} & ``The dataset generated and analyzed for this study will not be made publicly available due to patient privacy and lack of informed consent to allow sharing of patient data outside of the research team.''\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-8} & ``The datasets generated during and/or analyzed during the current study are not publicly available due to institutional restrictions on data sharing and privacy concerns. However, the data are available from the corresponding author on reasonable request.''\flagStyle{ } & Empty GitHub repository: ``Code coming soon \ldots'' paper says.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf R_{\mbox{\scriptsize c-empty}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-9} & ``The i2b2 data that support the findings of this study are available from i2b2 but restrictions apply to the availability of these data, which require signed safe usage and research-only. Data from UCSF are not available at this time as they have not been legally certified as being De-Identified, however, this process is underway and the data may be available by the time of publication by contacting the authors. Requesters identity as researchers will need to be confirmed, safe usage guarantees will need to be signed, and other restrictions may apply.''\flagStyle{ } & Basic documentation, very little comment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-10} & ``Not available due to restrictions in the ethical permit, but may be available on request.''\flagStyle{ } & Trivial comments, no documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-11} & ``The data that support the findings of this study are available in a deidentified form from Cleveland Clinic, but restrictions apply to the availability of these data, which were used under Cleveland Clinic data policies for the current study, and so are not publicly available.''\flagStyle{ } & ``We used only free and open-source software'' --- some of which is unspecified.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-12} & ``The i-ROP cohort study data for ROP is not publicly available due to patient privacy restrictions, though potential collaborators are directed to contact the study investigators \ldots''\flagStyle{ } & Not all code on GitHub, minor comments only.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{paper-usesRMarkdown} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code and example runs available in R Markdown.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\citenum{ref-14} & Data directly written into program code.\flagStyle{ } & Basic Matlab with routine comments.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{onlyPaperWithChecks} & Data available on Dryad plus publicly available data from the 1000 genomes project. Currently (apparently) for private view.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Code available for private view, though some code available with minor comments. Paper describes using two contrasting methods to help confirm correctness, ``As an additional check, I also coded the calculation of D based on a probabilistic approach, using genotype frequencies in each population to calculate the expected frequencies of each possible two-genotype combination (electronic supplementary material, table S1). Essentially identical results were obtained.'' --- but the contrasting method is not available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf S_{{\mbox{\scriptsize otherSE}}}$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-16} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Reasonaby commented code on Dryad, but code is not complete and presumably never checked.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-17} & On request.\flagStyle{ } & R, lightly commented.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ethics-paper} & No data required.\flagStyle{ } & Unrunnable incomplete code fragment.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_p$\hskip 3pt{}}\\
\citenum{ref-19} & Data embedded in PDF.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-20} & Data available on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Some comments, some code in Matlab.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_p$\hskip 3pt{}$\sf C_2$\hskip 3pt{}}\\
\citenum{ref-21} & Partial data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Documented R, including model's manual.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_3$\hskip 3pt{}}\\
\citenum{ref-22} & No data required.\flagStyle{ } & ``We constructed a bioeconomic model for an RSSF [restricted fishing effort small-scale fishery] using game theory'' for which results are discussed, yet no code is available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-23} & Data cited, not all available.\flagStyle{ } & Trivial documentation.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{example-numerical-error} & On Figshare.\flagStyle{ $\sf R_d$\hskip 3pt{}} & On Figshare, large amount of disorganised and undocumented code. Helpful features to make usable for third parties.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-25} & Data on Dryad.\flagStyle{ $\sf R_d$\hskip 3pt{}} & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-26} & Data on various web sites.\flagStyle{ } & No code available.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-27} & Data on request.\flagStyle{ } & ``The coding used to train the artificial intelligence model are dependent on annotation, infrastructure, and hardware, so cannot be released.'' (!) Algorithm (not source code) available on request.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-28} & Data on request.\flagStyle{ } & Python scripts can be requested.\flagStyle{ $\sf S_p$\hskip 3pt{}}\\
\citenum{ref-29} & Unspecified location on large website requiring registration.\flagStyle{ $\sf R_d$\hskip 3pt{}} & Has overall documentation but poorly commented Matlab code on GitHub.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\
\citenum{ref-30} & Available to researchers who meet criteria for access to confidential data.\flagStyle{ } & Despite the paper being a ``deep learning algorithm'' the code is not available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\
\citenum{ref-31} & Data access conditional on approved study proposal.\flagStyle{ } & Almost completely uncommented Python, but does have a basic setup script.\flagStyle{ $\sf R_c$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_1$\hskip 3pt{}}\\
\citenum{ref-32} & Unspecified locations on several large websites.\flagStyle{ } & Python used and apparently on GitHub, but --- an oversight? --- no code is available.\flagStyle{ $\sf S_{\mbox{\scriptsize NONE}}$\hskip 3pt{}}\\

### 2023-05-12 generated/info-for-main.tex
Don't delete .bbl files
Revisions for Computer Journal

\newlabel{supplementary-material-makefiles}{{11}{34}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{on-code-data-publication}{{12}{37}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{RAP-diagrams}{{12}{40}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{excelFigure}{{2}{40}{AAA}{BBB}{CCC}}
\newlabel{supplementary-Spiegelhalter-section}{{13}{40}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{survey-section}{{14}{43}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{supplementaryTableRepoSummary}{{4}{45}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{supplementary-journal-policies-section}{{14}{48}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{restrictive-policies}{{14}{52}{DUMMYA}{DUMMYB}{DUMMYC}}
\def\MaxMainPaperCitationNumber{0}

>>>>

\newlabel{supplementary-material-makefiles}{{9}{42}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{on-code-data-publication}{{10}{45}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{RAP-diagrams}{{10}{48}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{excelFigure}{{2}{48}{AAA}{BBB}{CCC}}
\newlabel{supplementary-Spiegelhalter-section}{{11}{48}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{survey-section}{{12}{51}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{supplementaryTableRepoSummary}{{4}{53}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{supplementary-journal-policies-section}{{12}{56}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{restrictive-policies}{{12}{60}{DUMMYA}{DUMMYB}{DUMMYC}}
\def\MaxMainPaperCitationNumber{126}

### 2023-05-12 generated/legend.tex
Revisions for Computer Journal

\begin{tabular}{lp{4.5in}}
\flagStyle{$\sf P_c$}&Journal has a code policy (see section~\ref{supplementary-journal-policies-section})\\
\flagStyle{$\sf P_{{\mbox{\scriptsize c-breach}}}$}&Paper breaches journal code policy (see section~\ref{supplementary-journal-policies-section})\\
\flagStyle{$\sf R_c$}&Paper uses a code repository (e.g., GitHub)\\
\flagStyle{$\sf R_{\mbox{\scriptsize c-empty}}$}&Code repository contains no code\\
\flagStyle{$\sf R_d$}&Paper uses a data repository (e.g., Dryad, Figshare, GitHub)\\
\flagStyle{$\sf S_{\mbox{\scriptsize NONE}}$}&No code available at all (note: code is not expected for standard models, systems or statistical methods)\\
\flagStyle{$\sf S_p$}&Paper says source code is available in principle\\
\flagStyle{$\sf S_{+}$}&Paper or URL provides source code\\
\flagStyle{$\sf S_{{\mbox{\scriptsize rigorous}}}$}&Evidence that source code was developed rigorously\\
\flagStyle{$\sf S_{\mbox{\scriptsize tested}}$}&Evidence that source code has been run with a clean build and tested\\
\flagStyle{$\sf S_{{\mbox{\scriptsize tools}}}$}&Evidence of any tool-based development\\
\flagStyle{$\sf S_{{\mbox{\scriptsize open source}}}$}&Team or open source development\\
\flagStyle{$\sf S_{{\mbox{\scriptsize otherSE}}}$}&Other evidence of good practice; see details in summary table\\
\flagStyle{$\sf C_0$}&Code has no non-trivial comments\\
\flagStyle{$\sf C_1$}&Code only has trivial comments (e.g., copyright)\\
\flagStyle{$\sf C_2$}&Helpful comments explaining code intent, rather than rephrasing the code\\
\flagStyle{$\sf C_{+}$}&Code has substantial, useful comments and documentation\\
\end{tabular}

>>>>

\begin{tabular}{lrp{4.5in}}
&\bfseries{Paper}&\\\bfseries{Flag}&\bfseries{count}&\bfseries{Meaning}\\ \hline 
\flagStyle{$\sf P_c$}&26&Journal has a code policy (see section~\ref{supplementary-journal-policies-section})\\ 
\flagStyle{$\sf P_{{\mbox{\scriptsize c-breach}}}$}&11&Paper breaches journal code policy (see section~\ref{supplementary-journal-policies-section})\\ 
\flagStyle{$\sf R_c$}&10&Paper uses a code repository (e.g., GitHub)\\ 
\flagStyle{$\sf R_{\mbox{\scriptsize c-empty}}$}&1&Code repository contains no code\\ 
\flagStyle{$\sf R_d$}&9&Paper uses a data repository (e.g., Dryad, Figshare, GitHub)\\ 
\flagStyle{$\sf S_{\mbox{\scriptsize NONE}}$}&12&No code available at all (note: code is not expected for standard models, systems or statistical methods)\\ 
\flagStyle{$\sf S_p$}&8&Paper says source code is available in principle\\ 
\flagStyle{$\sf S_{+}$}&12&Paper or URL provides source code\\ 
\flagStyle{$\sf S_{{\mbox{\scriptsize rigorous}}}$}&0&Evidence that source code was developed rigorously\\ 
\flagStyle{$\sf S_{\mbox{\scriptsize tested}}$}&0&Evidence that source code has been run with a clean build and tested\\ 
\flagStyle{$\sf S_{{\mbox{\scriptsize tools}}}$}&0&Evidence of any tool-based development\\ 
\flagStyle{$\sf S_{{\mbox{\scriptsize open source}}}$}&0&Team or open source development\\ 
\flagStyle{$\sf S_{{\mbox{\scriptsize otherSE}}}$}&1&Other evidence of good practice; see details in summary table\\ 
\flagStyle{$\sf C_0$}&10&Code only has comments unrelated to code intent (e.g., copyright)\\ 
\flagStyle{$\sf C_1$}&1&Code only has trivial or obvious comments\\ 
\flagStyle{$\sf C_2$}&3&Helpful comments explaining code intent, rather than rephrasing the code\\ 
\flagStyle{$\sf C_3$}&2&Code has substantial, useful comments, and documentation\\ 
\flagStyle{$\sf C_a$}&1&Code in repository uses assertions\\ 
\flagStyle{$\sf C_c$}&0&Code in repository uses pre- or post-conditions or similar\\ 
\end{tabular}
